A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-08-10 paper/paper1/ms.tex
Just made sure the overleaf is synced-- it is
This was the version submitted to arXiv (we had to turn off linenumbers)
whitespace changes and had to keep intermediate bbl for submission
Addressing the referee report

\documentclass[linenumbers, twocolumn]{aastex631}
\bibliographystyle{aasjournal}

@@

% This is the version destined for Overleaf on June 7th, 2023.
\title{A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation}

@@

\author[0000-0001-9626-0613]{Daniel M. Krolikowski}
\affil{\Steward}
%\affil{\UTAustin}

@@

% This is the submitted version: July 13, 2023 at 3:13 pm central 
% Revised at 3:31 pm to have a shorter abstract

@@

% Describe construction of residual spectra

@@

\subsection{Cause for stellar modulation}
As discussed in Section \ref{TESSmodulation}, the \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $P=4.7-5.9$ days. Some sectors exhibit lower amplitudes.  The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.  The cause for such orbital and rotational synchronization would then be either coincidence or secular star-planet tidal interactions.  For the latter, disk migration could have naturally ceased near the co-rotation radius, leaving the planet to reside naturally near the stellar $P_\mathrm{rot}$.

>>>>

\documentclass[linenumbers, twocolumn, trackchanges]{aastex631}
\bibliographystyle{aasjournal}

@@

\title{A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation}

@@

\author[0000-0001-9626-0613]{Daniel M. Krolikowski}
\affil{\Steward}

@@

% This is the submitted version: July 13, 2023 at 3:13 pm central
% Revised at 3:31 pm to have a shorter abstract !

@@

@@

\subsection{Cause for stellar modulation}
As discussed in Section \ref{TESSmodulation}, the \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $P=4.7-5.9$ days. Some sectors exhibit lower amplitudes.  The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage\edit1{s}---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8-day orbital period of planet b.  The cause for such orbital and rotational synchronization would then be either coincidence or secular star-planet tidal interactions.  For the latter, disk migration could have naturally ceased near the co-rotation radius, leaving the planet to reside naturally near the stellar $P_\mathrm{rot}$.
